\documentclass{recipecard}
\begin{document}
\vspace{8pt}

\ingredient{1/2 cup chopped white onion}
\ingredient{1 cup  5 cheeses: Provolone, Romano, Mozzarela, Asiago, Parmesan}
\ingredient{3 1/2 tablespoons of Pure Sesame Oil}
\ingredient{1/2 cup  Basil Leaves}
\ingredient{3 tablespoons Lemon Pepper}
\ingredient{2 1/2 cups of Whole Wheat Flour}
\ingredient{Non-stick spray Canola oil}
\ingredient{1/2 cup Sunflower seed kernels sea salt}
\ingredient{1/4 Yellow Squash}
\ingredient{1/4 Eggplant}
\ingredient{1/2 cup sliced mushrooms}
\ingredient{1 Active Dry Yeast}
\ingredient{1/3 - 1/2 Garlic clove}
\ingredient{2 tablespoons Peppercorn}
\ingredient{3 No calorie stevia extract packets}

\begin{recipe}{Garlic Eggplant Polygonal Cheese Bread with Basil Leaves}{} \textbf{(1)} Mix 1 cup warm water with packet active dry yeast, 3 1/2 tablespoons of seasame oil, 2 or 3 packets Stevia ,1 cup Wheat Flour and 1/2 cup sunflower seeds \textbf{(2)}. Mix with cooking chopsticks in a medium bowl or Tupperware container.\textbf{ (3)}. Add 1/2 cup of water and 1 cup of flour add additional tablespoons of water in center dough until desired baker's ratio is achieved. \textbf{(4)}. Kneed dough and then let sit for a few minutes. \textbf{(5)}. Wash bowl with attention and preheat oven 400 degrees \textbf{(6)}. Chop onion and garlic. \textbf{(7)}. Slice eggplant and squash into desired conic sections. \textbf{(8)}. Examine dough and place a couple of valleys or saddles in the dough and fill with some oil, sugar (or honey) and flour. \textbf{(9)}. Kneed a second time and spray the large circular pan with Canola oil. \textbf{(10)}. Make a k-regular polygon shape with the dough on pan with desired thickness. \textbf{(11)}. Place a layer of Basil leaves on the surface.\textbf{ (12)}. Roll up the edge of polygon to form ridges to desired height maximization .\textbf{ (13)}. Place 1 half packet of sugar on the edge of polygon. \textbf{(14)}. Place eggplant, squash and mushrooms on the interior of the polygon with concentric circles.\textbf{ (15)}. Add another layer of Basil, peppercorn, lemon pepper. \textbf{(16)}. Sprinkle the chopped garlic with a uniform distribution of points.\textbf{ (17)}. Add cheese working from the center of polygon outward and layer amount.\textbf{ (18)}. Add final layer of basil leaves. \textbf{(19)}. Place in the oven for 12-15 minutes and check three times in decreasing temporal intervals with one chopstick.\textbf{ (20)}. Serve Garlic Eggplant Polygonal Cheese Bread with Basil Leaves. Hope you enjoy. \cookingtime{12-15 min.}
	\cooktemp{400}{F}
\end{recipe}

\end{document}
